---
title: "Systematic_Map_Bibliometrix_Sample"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Firstly, load in bibliometrix package
```{r}
library(bibliometrix)

```

Import bibtex file - exported sample from Scopus. The convert2df() function converts the bibtex file into a bibliometrix dataframe

```{r}
bib_sample <- convert2df("systematic_map_scopus_sample.bib",dbsource = "scopus", format = "bibtex")

View(bib_sample)
```

Note that column bib_sample$AU contains authors of each paper (as surnames and initials) separated by semicolon (;). We can easily split these strings and extract a list of all author names to a vector:

```{r}
authors <- bib_sample$AU 
 head(authors) 
 authors <- unlist(strsplit(authors, ";")) 
 authors <- authors[order(authors)]
 head(authors)
```

Preliminary descriptive analysis 
```{r}
bib_sample_results <- biblioAnalysis(bib_sample, sep = ";")
```

Plot of analysis 
```{r}
plot(bib_sample_results, k = 10, pause=TRUE)
```

Using the function citations() we can generate frequency table of most cited authors

```{r}
most_cited_authors <- citations(bib_sample, field = "author", sep = ";")
cbind(most_cited_authors$Cited[1:10])
```

Using the localCitations() we can look at local citations which are citations within the dataset, in this case the sample 

```{r}
most_cited_authors_local <- localCitations(bib_sample, sep = ";")
most_cited_authors_local$Authors[1:10,]
```

Using biblioNetwork() we can do bibliographic coupling between authors
```{r}
NetMatrix <- biblioNetwork(bib_sample, analysis = "coupling", network = "authors", sep = ";")
net = networkPlot(NetMatrix, weighted = NULL, n = 10, Title = "Authors' bibliographic coupling", type = "fruchterman", size = 5, remove.multiple = TRUE, labelsize = 0.8)

```


Using biblioNetwork() we can do bibliographic collaboration between authors
```{r}
NetMatrix <- biblioNetwork(bib_sample, analysis = "collaboration", network = "authors", sep = ";")
net <- networkPlot(NetMatrix, weighted = NULL, n = 10, Title = "Authors' collaborations", type = "fruchterman", size = 5, remove.multiple = TRUE, labelsize = 0.5)
```

Country Collaborations - visualise which countries publish together most frequently
```{r}
bib_sample <- metaTagExtraction(bib_sample,Field = "AU_CO", sep = ";")
NetMatrix <- biblioNetwork(bib_sample, analysis = "collaboration", network = "countries", sep = ";")
net <- networkPlot(NetMatrix, n = 10, Title = "Country Collaboration", type = "auto", size = TRUE, remove.multiple = FALSE, labelsize = 0.5)
```


Keyword co-occurrences - visualise which papers share most keywords
```{r}
NetMatrix <- biblioNetwork(bib_sample, analysis = "co-occurrences", network = "keywords", sep = ";")
net <- networkPlot(NetMatrix, n = 25, Title = "Keyword co-occurance", type = "fruchterman", size = T, remove.multiple = FALSE, labelsize = 0.7, edgesize = 5)
```

Author keywords - words chosen by the author to best reflect the paper 
```{r}
NetMatrix <- biblioNetwork(bib_sample, analysis = "co-occurrences", network = "author_keywords", sep = ";")
net <- networkPlot(NetMatrix, n = 25, Title = "Keyword co-occurance", type = "fruchterman", size = T, remove.multiple = FALSE, labelsize = 0.7, edgesize = 5)

```

Historical citation network - chronological network map 
```{r}
bib_sample_histresults <- histNetwork(bib_sample,min.citations = 10, sep = ";")
net <- histPlot(bib_sample_histresults, labelsize = 2)
```


